Personality and political beliefs across the lifespan

### 2019-11-19 scripts/manuscript.Rmd
figure1 personality traits across the lifespan)

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize()
```

@@

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

>>>>

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize() %>% 
  mutate(age = as.numeric(age))
```

@@

```{r figure1}
ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "Age", y = "How strongly participants identify with the personality trait", 
       color = "Personality Trait")+
  theme_classic()+
  scale_color_manual(values = c("red", "orange", "yellow","green", "blue"),
                     labels=c("Agreeableness", "Conscientiousness", 
                              "Emotional Stability", "Extraversion",
                             "Openness to experiences"))

```
# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### 2019-11-19 scripts/manuscript.tex
figure1 personality traits across the lifespan)

\section{Methods}\label{methods}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.

@@

>>>>

\includegraphics{manuscript_files/figure-latex/figure1-1.pdf} \# Methods
We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych}
(Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \&
Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \&
Francois, 2018), \emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper,
\& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b),
\emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr}
(Version 1.0.0; Wickham \& Henry, 2019), and \emph{tidyverse} (Version
1.2.1; Wickham, 2017) for all our analyses.

@@

\hypertarget{ref-R-psych}{}
Revelle, W. (2018). \emph{Psych: Procedures for psychological,
psychometric, and personality research}. Evanston, Illinois:
Northwestern University. Retrieved from
\url{https://CRAN.R-project.org/package=psych}
